Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-14 paper/paper.tex
finalizando passada...

\subsection{Characterization of Test Suites}

To provide a brief overview of the test suites and understand if the engines
have specific testing purposes, we investigated the most common
objects and functions that each one of the JS engines employ.
To achieve this goal, we started by filtering out many non-relevant source
code statements available on the test suites. We started by removing JS language constructs (such as \textt{if}, \textt{for}, and \textt{var}). We then removed
special characters (such as parentheses, mathematical symbols, and semicolons).
For the remaining source code constructs, we search for the ``.'' character, which
indicates a function call. We then stored the function and the object that host
that function.  By manually analyzing this data, we noted many general purpose
functions, that do not provide any hint on the kind of behavior the engine is
more likely to test (such as \texttt{console.log}). We also removed these
general purpose functions. The remaining object/functions are shown at
Figure~\ref{fig:histograms}.

\begin{figure}[thp]
\begin{center}
$
\begin{array}{cc}
Charka & Duktape \\
\includegraphics[width=.5\textwidth, clip, trim= 0px 35px 10px 0px]{figs/hist/chakra.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/duktape.pdf} \\
Hermes & JerryJS \\
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/hermes.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jerryJS.pdf} \\
JSI & Test262 \\
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jsi.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/test262.pdf} \\
TinyJS & V8 \\
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/tinyJS.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/v8.pdf} \\
\end{array}
$
\end{center}
\caption{histograms.}
\label{fig:histograms}
\end{figure}

@@

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \hermes & \percentSuiteTestHermes{} \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

@@

\begin{center}
  \fbox{
    \begin{minipage}{11cm}
      \textit{Summary:}~Most of the engines seem to adhere well to the
      \js\ standard. Except for \hermes and \chakra, the passing ratio of all
      engines is above 90\%.
      \end{minipage}
    }
\end{center}

@@

\Fix{
In particular, we were not able to reuse the \smonkey tests on the
\hermes engine. This happened because \smonkey has its own assertion
framework, but \hermes did not interpret these assertions, resulting
in failures in all test executions from this engine. These failures
did not happen when the \smonkey tests were transplanted to the other engines,
though.
}
\Gustavo{Falar pq Hermes nao esta na tabela}

>>>>

@@

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \veight{} & \percentSuiteTestVeight{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \jsc & \percentSuiteTestJSC{}\\
    \chakra{} & \percentSuiteTestChakra{} \\
    %\hermes & \percentSuiteTestHermes{} \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

@@

\begin{center}
  \fbox{
    \begin{minipage}{11cm}
      \textit{Summary:}~Most of the engines seem to adhere well to the
      \js\ standard. Except for \chakra, the passing ratio of all
      engines is above 90\%.
      \end{minipage}
    }
\end{center}

@@

In particular, we were not able to reuse the \smonkey tests on the
\hermes engine. This happened because \smonkey has its own assertion
framework, but \hermes did not interpret these assertions, resulting
in failures in all test executions from this engine. These failures
did not happen when the \smonkey tests were transplanted to the other engines,
though.
